Inference failure: Confound and control in BBS experiments

### 2016-04-14 response.md

# Response to reviewers

We thank both reviewers for the insightful discussions.
Beyond their overall encouragement, they have identified terminological and conceptual errors on our parts and given additional methodological advice for which we are very grateful.
We note the reviewers were largely in agreement with regards to their overall evaluation and particular criticisms.
We have found it straight-forward to include all of their advice, and think this has greatly improved the manuscript.

In particular, reviewer #1 has pointed out that we employed the term parameter not only in the sense of e.g. a population parameter with which inference is concerned, but also incorrectly to refer to factors ("nuisance parameter").
In the reworked version of the manuscript, the term parameter is only employed in the sense of a population parameter to be estimated.
We have also corrected the other confusingly written or wrong uses of statistical terminology and concepts, such as those concerning variance in parameter estimation via multiple regression (which reviewer #2 has also pointed out).

Reviewer #2 (Jake Westfall) inquires about quantitative estimates of the failure rates of this approach.
We have amended the methods section with a short simulation, where we show that in the described procedure, in realistic contexts, failures (e.g. failures to reject confounded samples when a significant effect is only observed due to confounding) occur more often than correct rejections (e.g. correctly rejecting a sample for confound imbalance).

We have also rephrased multiple sections, shortened the discussion of collinearity, extended the discussions of the error of "accepting" the null, further emphasized the importance of providing descriptive statistics (which both reviewers have repeatedly asked for), reworked and shortened the confusingly written section on employing multiple regression to control for confounds (including a reference to Westfall & Yarkoni, 2016, which appeared just days after our initial submission).

### 2016-05-09 simulation/statfail.Rmd
parameter for number of cores in multiprocessing

---
title: 'Inference failure: Confound and control in BBS experiments'
author: "Phillip M. Alday"
date: "May  2016"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    self_contained: TRUE
    highlight: textmate
params:
  n: 500
  use_plotly: FALSE
---

@@

# use some parallel magic to speed things long
library(parallel)
options(mc.cores=2)
library(doMC)
library(foreach)
registerDoMC(2)

>>>>

---
title: 'Inference failure: Confound and control in BBS experiments'
author: "Phillip M. Alday"
date: "May  2016"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    self_contained: TRUE
    highlight: textmate
params:
  n: 500
  use_plotly: FALSE
  cores: 2
---

@@

# use some parallel magic to speed things long
library(parallel)
options(mc.cores=params$cores)
library(doMC)
library(foreach)
registerDoMC(params$cores)
